Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-03-10 analysis/paper/paper.qmd
stash

ggplot(tcsa,
        aes(0.3, 
            min_tcsa)) +
  # show regions for tools from Lomabrd 2021 & 2022
  # https://www-sciencedirect-com.offcampus.lib.washington.edu/science/article/pii/S0277379121002286
  # https://assets.researchsquare.com/files/rs-2016964/v1/00d381a3-3ecf-4d5b-b2ec-89a41227bbd5.pdf?c=1662475267
    annotate("rect", 
           xmin = 0.1,
           xmax = 0.2,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned arrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = point_function_group_label_y,
           y = (18-4) /2 + 4) +
      annotate("rect", 
           xmin = 0.2,
           xmax = 0.3,
           ymin = 17,
           ymax = 47,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Un-poisoned arrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = point_function_group_label_y,
           y = (47-17) /2 + 17) +
      annotate("rect", 
           xmin = 0.3,
           xmax = 0.4,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           x = point_function_group_label_y,
           y = (76-40) /2 + 40 - 5) +
      annotate("rect", 
           xmin = 0.4,
           xmax = 0.5,
           ymin = 42,
           ymax = 90,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin tips",
               hjust = 0,
           x = point_function_group_label_y,
           y = (90-42) /2 + 42 ) +
     annotate("rect", 
           xmin = 0.5,
           xmax = 0.6,
           ymin = 80,
           ymax = 200,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Stabbing spear tips",
               size = point_function_group_label_size,
               hjust = 0,
               lineheight = 0.75,
           x = point_function_group_label_y,
           y = (200-80) /2 + 80 ) +
  geom_boxplot(alpha = 0.1) +
  geom_quasirandom(alpha = 0.4,
                   size = 0.7) +
  coord_cartesian(xlim = c(-0.1,1)) +
  theme_bw(base_size = 6) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()
        ) +
  labs(y = "TCSA")

# ggsave(here::here("analysis/figures/fig-tcsa-all-sp.png"),
#        width = 4.45,
#        height = 4.5,
#        units = "in")

@@

# ggsave(here::here("analysis/figures/fig-artifact-size-cluster.png"),
#        width = 4,
#        height = 4,
#        units = "in")

@@

# ggsave(here::here("analysis/figures/fig-tcsa-raw-materials.png"),
#        width = 4.3,
#        height = 2.7,
#        units = "in",
#        bg = "white")

@@

ggplot(tcsa_mass_no_na,
       aes(`Weight(g)`,
           min_tcsa,
           colour = raw_materials_top)) +
  geom_point(size = 1.5) +
    labs(x = "Weight (g)", 
       y = "TCSA",
       colour='Raw material') +
  geom_smooth(method=lm, se=FALSE, size = .7)+
  theme_bw(base_size = 10) +
  theme(
  legend.title = element_text(size = 6.3),
  legend.text = element_text(size = 5.3),
  legend.position = c(.8,.3),
  legend.key.height = unit(4.8, 'mm'),
  legend.key.width = unit(2.5, 'mm'))

# ggsave(here::here("analysis/figures/fig-tcsa-size.png"),
#        width = 4,
#        height = 3.3,
#        units = "in")

@@

# ggsave(here::here("analysis/figures/fig-tcsa-radio-carbon.png"),
#        width = 4,
#        height = 4.5,
#        units = "in",
#        bg = "white")

@@

 ggplot(tcsa_site,
              aes(y = min_tcsa, 
                  x = label_site)) +
  geom_boxplot() +
  theme_minimal() +
  labs(x = "", 
       y = "TCSA") +
  theme(axis.text.x = element_text(size = 5)) +
  scale_x_discrete(guide = guide_axis(angle = 45))+
  geom_quasirandom(alpha = 0.4,
                   size = 1.6)+
   annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 17,
           ymax = 47,
           fill = "blue",
           alpha = 0.2) +
      annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 42,
           ymax = 90,
           fill = "purple",
           alpha = 0.2) +
     annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 80,
           ymax = 200,
           fill = "yellow",
           alpha = 0.2)

# ggsave(here::here("analysis/figures/fig-tcsa-per-sites.png"),
#        width = 4.3,
#        height = 3,
#        units = "in",
#        bg = "white")
```

@@

# ggsave(here::here("analysis/figures/fig-gis-tcsa-sitess.png"),
#        width = 4,
#        height = 6,
#        units = "in",
#        bg = "white")

>>>>

ggplot(tcsa,
        aes(0.3, 
            min_tcsa)) +
  # show regions for tools from Lomabrd 2021 & 2022
  # https://www-sciencedirect-com.offcampus.lib.washington.edu/science/article/pii/S0277379121002286
  # https://assets.researchsquare.com/files/rs-2016964/v1/00d381a3-3ecf-4d5b-b2ec-89a41227bbd5.pdf?c=1662475267
    annotate("rect", 
           xmin = 0.1,
           xmax = 0.2,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Poisoned arrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = point_function_group_label_y,
           y = (18-4) /2 + 4) +
      annotate("rect", 
           xmin = 0.2,
           xmax = 0.3,
           ymin = 17,
           ymax = 47,
           fill = "blue",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Un-poisoned arrow tips",
               hjust = 0,
               lineheight = 0.75,
           x = point_function_group_label_y,
           y = (47-17) /2 + 17) +
      annotate("rect", 
           xmin = 0.3,
           xmax = 0.4,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Dart tips",
               hjust = 0,
           x = point_function_group_label_y,
           y = (76-40) /2 + 40 - 5) +
      annotate("rect", 
           xmin = 0.4,
           xmax = 0.5,
           ymin = 42,
           ymax = 90,
           fill = "purple",
           alpha = 0.2) +
      annotate("text", 
               size = point_function_group_label_size,
               label = "Javelin tips",
               hjust = 0,
           x = point_function_group_label_y,
           y = (90-42) /2 + 42 ) +
     annotate("rect", 
           xmin = 0.5,
           xmax = 0.6,
           ymin = 80,
           ymax = 200,
           fill = "yellow",
           alpha = 0.2) +
      annotate("text", 
               label = "Stabbing spear tips",
               size = point_function_group_label_size,
               hjust = 0,
               lineheight = 0.75,
           x = point_function_group_label_y,
           y = (200-80) /2 + 80 ) +
  geom_boxplot(alpha = 0.1) +
  geom_quasirandom(alpha = 0.4,
                   size = 0.7) +
  coord_cartesian(xlim = c(-0.1,1)) +
  theme_bw(base_size = 6) +
  theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()
        ) +
  labs(y = "TCSA")
```

@@

@@

@@

ggplot(tcsa_mass_no_na,
       aes(`Weight(g)`,
           min_tcsa,
           colour = raw_materials_top)) +
  geom_point(size = 1.5) +
    labs(x = "Weight (g)", 
       y = "TCSA",
       colour='Raw material') +
  geom_smooth(method=lm, se=FALSE, size = .7)+
  theme_bw(base_size = 10) +
  theme(
  legend.title = element_text(size = 6.3),
  legend.text = element_text(size = 5.3),
  legend.position = c(.8,.3),
  legend.key.height = unit(4.8, 'mm'),
  legend.key.width = unit(2.5, 'mm'))
```

@@

@@

 ggplot(tcsa_site,
              aes(y = min_tcsa, 
                  x = label_site)) +
  geom_boxplot() +
  theme_minimal() +
  labs(x = "", 
       y = "TCSA") +
  theme(axis.text.x = element_text(size = 5)) +
  scale_x_discrete(guide = guide_axis(angle = 45))+
  geom_quasirandom(alpha = 0.4,
                   size = 1.6)+
   annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 4,
           ymax = 18,
           fill = "green",
           alpha = 0.2) +
      annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 17,
           ymax = 47,
           fill = "blue",
           alpha = 0.2) +
      annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 40,
           ymax = 76,
           fill = "orange",
           alpha = 0.2) +
      annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 42,
           ymax = 90,
           fill = "purple",
           alpha = 0.2) +
     annotate("rect", 
           xmin = 7.5,
           xmax = 8,
           ymin = 80,
           ymax = 200,
           fill = "yellow",
           alpha = 0.2)
```

@@
